



The  problem   of  allocating   cloud  resources   in  performant,   robust  and
energy-efficient ways is  of paramount importance in today's  usage of computing
infrastructures, and a number of research papers have contributed new allocation
techniques to  address this issue.   A pitfall of research  on IaaS lies  in the
validation of the models and algorithms proposed, which requires infrastructures
that are difficult to set up for individual researchers.  As a consequence, many
researchers evaluate their work through  simulation. A number of simulators have
been  developed for  that purpose  (\cite{CalheirosRBRB11,KliazovichBK12}).  They  are typically  based on
discrete-event simulation,  using models  for each  elementary component  of the
infrastructure,  which  are then  composed  to  simulate  the whole  system  and
applications running on it.  This approach is attractive from the infrastructure
provider  perspective  since the  simulated  system  can be  finely  customized.
However, such  an \textit{ab  initio} construction  poses a  significant problem
regarding  the  calibration  and  validation   of  the  composed  model  against
real-world  measurements.    Another  approach   is  the  simulation   from  the
client-side (from the application perspective),  which can specifically focus on
the prediction of a couple of metrics, such  as the makespan and the cost of the
application.  It is  noticeable that the research papers  adopting a client-side
view  generally include  an evaluation  of the  simulation through  experimental
studies, while such  an evaluation is generally  missing for infrastructure-wide
simulators.

Altough much  fewer works  address the simulation  from the  client perspective,
several very  different methods have  been proposed  to reach this  goal.  Among
these    works,     detailed    in    the    related     work    section,    are
EMUSIM~\cite{CalheirosNRB13}  that  use   emulation,  PICS~\cite{KimWH15}  which
implemens  a simplified  discrete  event  simulator, and~\cite{PucherGWK15}  who
build a statistical model from observations.


In this  paper, we study the  simulation also from the  application perspective,
using  the   discrete  event  simulation  toolkit   SimGrid~\cite{simgrid08}  to
implement our model. We assume an  automated process making the provisioning and
scheduling decisions  on behalf the  user on  the real infrastructure.   To that
purpose,  we   use  \emph{Schlouder}  \cite{},  a   client-side  cloud  resource
broker. This  paper's contribution  is twofold:
\begin{itemize}
\item We propose a simulation tool
\item We make an  in-depth analysis  of the
factors that impact the simulation accuracy,  and in this regard go further than
the related works. We analyze the sensitivity of several parameters, among which
the  impact  of   the  job  submission  management  overheads,   the  effect  of
inaccuracies in the job execution times specified  by the user, or the boot time
of  VMs.  The  study is  carried out  on several  use cases  which comprise  two
different type  of applications (workflow  and bag-of-tasks), with  several size
instances for  each of them, and  each application is operated  on two different
type of infrastructure (private and public).
\end{itemize}

....

We advocate  that a precise assessment  of simulation
should be  carried out against real  execution figures to better  understand the
limits  of simulation  applicability. 

The paper is organized as follows : ....


\begin{comment}
These scheduling algorithms of Schlouder have been reimplemented in a simulation
system,  based on  the simulation  toolkit SimGrid~\cite{simgrid08}.   Our study
aims to isolate the different  parameters that influence the simulation accuracy
and what  degree of divergence  between real  execution and simulation  might be
expected in each case.
\end{comment}





\begin{comment}
[9] R. N. Calheiros, R. Ranjan, A. Beloglazov, C. A. D. Rose, and R. Buyya, “CloudSim: a toolkit for modeling and simulation of cloud computing environments and evaluation of resource provisioning algo- rithms,” Software: Practice and Experience, vol. 41, no. 1, pp. 23–50,
2011.
[10] D. Kliazovich, P. Bouvry, and S. U. Khan, “GreenCloud: a packet-level simulator of energy-aware cloud computing data centers,” The Journal of Supercomputing, vol. 62, no. 3, pp. 1263–1283, 2012.

[11] B. Wickremasinghe, R. N. Calheiros, and R. Buyya, “Cloudanalyst: A CloudSim-based visual modeller for analysing cloud computing environments and applications,” in Advanced Information Networking
and Applications (AINA), 2010 24th IEEE International Conference on.
IEEE, 2010, pp. 446–452.

[12] S. K. Garg and R. Buyya, “Networkcloudsim: Modelling parallel applications in cloud simulations,” in Utility and Cloud Computing
(UCC), 2011 Fourth IEEE International Conference on. IEEE, 2011,
pp. 105–113.

[13] M. Tighe, G. Keller, M. Bauer, and H. Lutfiyya, “DCSim: A data centre simulation tool for evaluating dynamic virtualized resource management,” in Network and service management (cnsm), 2012 8th
international conference and 2012 workshop on systems virtualiztion
management (svm), Oct 2012, pp. 385–392.

[14] S. K. S. Gupta, R. Gilbert, A. Banerjee, Z. Abbasi, T. Mukherjee, and G. Varsamopoulos, “GDCSim: A tool for analyzing Green Data Center design and resource management techniques,” in Green Computing
Conference and Workshops (IGCC), 2011 International, July 2011, pp.
1–8.
\end{comment}

 


\section{Related Work}

EMUSIM combines  emulation and  simulation to extract  information automatically
from  the application  behavior (via  emulation)  and uses  this information  to
generate the  corresponding simulation  model. Such a  simulation model  is then
used  to  build  a simulated  scenario  that  is  closer  to the  actual  target
production  environment   in  terms   computing  resources  available   for  the
application and request patterns.
- EMUSIM operates uniquely with information that is available for customers of public IaaS providers
- Automated Emulation Framework (AEF) [2] for emulation and CloudSim [3] for simulation
- emulation : run the actual software on a subset of the hardware (=hardware model)
- application BoT
